MCC Models

### 2019-04-05 papers/full_paper/manuscript.Rmd
first draft full paper
prune frequentist models to avoid singular fit

abstract: |
  Language is used and learned in complex social settings. To infer what a speaker means, listeners have to go beyond the literal meaning of words and rely on pragmatic inferences. During language acquisition, the same processes can help children to learn the meaning of novel words. Yet, pragmatic inferences require balancing multiple sources of social information. Here we study this integration process. We isolate two types of pragmatic inference and formalize how they should be integrated in a Bayesian pragmatics model. We present a series of experiments with preschool children and adults that suggest that information integration is best described as a form of probabilistic inference.

@@

# model
lm_ex1 <- glmer(correct ~ condition +
              (condition |id) + (condition |agent), 
              data = adult_ex1_data, 
              family = binomial,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

@@

# model (maximally converging)
lm_ex2pref <- glmer(correct ~ condition +
              (1|id) + (condition |agent), 
              data = adult_ex2_preference_data, 
              family = binomial,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

@@

# model
lm_ex2nov <- glmer(correct ~ condition +
              (1|id) + (condition |agent), 
              data = adult_ex2_novelty_data, 
              family = binomial,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

@@

```{r ex3 GLMM, cache=T}
# model 
lm_ex3 <- glmer(correct_inf ~ common_ground_manipulation*speaker*alignment + (speaker+alignment|id) + (speaker+alignment|agent), 
              data = adult_ex3_data, family = binomial, 
              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

@@

lm_ex4_strong <- glmer(correct_inf ~ common_ground_manipulation*speaker*alignment + (speaker+alignment|id) + (speaker+alignment|agent), 
              data = adult_ex4_data %>% filter(prior_manipulation == "strong"), family = binomial, 
              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

@@

lm_ex4_medium <- glmer(correct_inf ~ common_ground_manipulation*speaker*alignment + (speaker+alignment|id) + (speaker+alignment|agent), 
              data = adult_ex4_data %>% filter(prior_manipulation == "medium"), family = binomial, 
              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

@@

lm_ex4_weak <- glmer(correct_inf ~ speaker*alignment + (speaker+alignment|id) + (speaker+alignment|agent), 
              data = adult_ex4_data %>% filter(prior_manipulation == "weak"), family = binomial, 
              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

@@

child_ex3_lm <- glmer(correct_inf ~ age_num*speaker*alignment 
      + (speaker*alignment | id) 
      + (age_num*speaker*alignment | agent), 
      family = "binomial",
      data = child_ex3_lm_data,
      control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

#summary(child_ex3_lm)

>>>>

abstract: |
  Language is used and learned in complex social settings. To infer what a speaker means, listeners have to go beyond the literal meaning of words and rely on pragmatic inferences. During language acquisition, the same processes can help children to learn the meaning of novel words. Yet, pragmatic inferences require balancing multiple sources of social information. Here we study this integration process. We isolate two types of pragmatic inference and formalize how they should be integrated according to a Bayesian pragmatics model. We present a series of experiments with preschool children and adults that suggest that information integration is best described as a form of probabilistic inference.

@@

# model
lm_ex1 <- glmer(correct ~ condition +
              (1 |id) , 
              data = adult_ex1_data, 
              family = binomial,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

#summary(lm_ex1)

@@

# model (maximally converging)
lm_ex2pref <- glmer(correct ~ condition +
              (1|id), 
              data = adult_ex2_preference_data, 
              family = binomial,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

#summary(lm_ex2pref)

@@

# model
lm_ex2nov <- glmer(correct ~ condition +
              (condition|id), 
              data = adult_ex2_novelty_data, 
              family = binomial,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

#summary(lm_ex2nov)

@@

```{r ex3 GLMM, cache=T}
# model 
lm_ex3 <- glmer(correct_inf ~ common_ground_manipulation*speaker*alignment + (alignment|id), 
              data = adult_ex3_data, family = binomial, 
              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

@@

lm_ex4_strong <- glmer(correct_inf ~ common_ground_manipulation*speaker*alignment + (speaker+alignment|id), 
              data = adult_ex4_data %>% filter(prior_manipulation == "strong"), family = binomial, 
              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

@@

lm_ex4_medium <- glmer(correct_inf ~ common_ground_manipulation*speaker*alignment + (alignment|id), 
              data = adult_ex4_data %>% filter(prior_manipulation == "medium"), family = binomial, 
              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

@@

lm_ex4_weak <- glmer(correct_inf ~ speaker*alignment + (speaker+alignment|id), 
              data = adult_ex4_data %>% filter(prior_manipulation == "weak"), family = binomial, 
              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

@@

child_ex3_lm <- glmer(correct_inf ~ age_num*speaker*alignment 
      + (speaker+alignment | id), 
      family = "binomial",
      data = child_ex3_lm_data,
      control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

summary(child_ex3_lm)
